Mamary Gland Development Exploratory Data Analysis

### 2017-06-27 src/QCAnalysis.Rmd
minor updates

pD <- mutate(pD,
	     PassViability=prcntMito < ThresholdViability,
	     PassGenesDet=GenesDetected > ThresholdGenesDet,
	     PassLibSize=UmiSums > ThresholdLibSize,
	     PassAll= PassViability & PassGenesDet & PassLibSize)
table(pD$PassViability,pD$SampleID)
table(pD$PassGenesDet,pD$SampleID)
table(pD$PassLibSize,pD$SampleID)
table(pD$PassAll,pD$SampleID)

>>>>

pD <- mutate(pD,
	     PassViability=prcntMito < ThresholdViability,
	     PassGenesDet=GenesDetected > ThresholdGenesDet,
	     PassLibSize=UmiSums > ThresholdLibSize,
	     PassAll= PassViability & PassGenesDet & PassLibSize & bc.obs.Freq==1)
table(pD$PassViability,pD$SampleID)
table(pD$PassGenesDet,pD$SampleID)
table(pD$PassLibSize,pD$SampleID)
table(pD$PassAll,pD$SampleID)
